% A local newspaper writes a stories about Cris's
% climbing gym being a dating scene.
% Cris & the poet go to the climbing gym
% and sneak in to the medical school pool,
% which is peaceful before a swim practice interrupts it.

The local network covered Cris's gym. \\
Reporter came around,  \\
Everyone was real excited. 

She said, You're our new leder:  \\
Climbing is the new Tinder. \\
The youth were meeting in person, \\
It was a big story. 

It was a global trend; maybe you caught it. \\
We went and watched them work their form-- \\
We went and watched them work their routes--

And build their bodies. Some attempted ledger-record, \\
Testing Heavens; Some gave lessons-- \\
To pretty girls-- \\
And others grew their grip strength. 

And when the weather was good, \\
Sneaking in to medical school, \\
To use its pool, \\
Peering through the windows long the path; \\
Lessons learned on grappling mats, \\
Strength in opposition training; \\
Girls \& boys in volley courts for \\
\quad trophied golden \\
\qquad coated brass...

Green oasis waters: emptytranquil, \\
\quad sun-warmed waters. \\
Then the clockstrike, with its \\ 
Thundercampaign timbre, \\
And its mass migration.

First, the piscine plain is \\
Subdivided / so: the open / water's made to \\
Lanes by stretched \& twining wireflow, \& \\
Swimmers take their place by speed \& \\
Space is hieraraquí'd. \\
How easily we come to share \\
When lines are laid on pavement bare.

Or stand erect in humus soil \\
Letting life know air.