% His first night, the protagonist drinks in a young trendy neighborhood
% and people watches while chatting and sharing litrãon of beer with his
% Brazilian friend.

% The poet goes home and wanders the streets. 
% He encounters some of the desperation and madness of a city of sin.
% He retreats to his laptop and reads Frank O'Hara's Personism manifesto.

% ExqSci status: SUBMERGED

Up all night that night at \\
Plastic tables, round red tables \\
Kicking back \& clinking glasses with the \\
Little cups, that make litrãos seem so abundant.

Myself a dark-eyed junko down at Barra Funda, \\
Watching wildlife the milling \\
Rites while Toby reads the room, like David  \\
Attenborough, Austen, Doyle: \\
Footwear, fannypack, the styled assets...

--Couple'a feelers, bottle of fizz-- \\
--Headin' for boilin', simmerin' rizz.--

You get a sense at once, he says-- \\
The head-to-toe assembled parts. \\
Harmony in poetry, I link \& show a spectogram-- \\
My words the bassy din and many tongues did swallow, \\
As I strained to tell of prairie dogs, \\
Who yip a sentence in an instant \\
Vertisplayed as chord.

--All the girls in little black dresses \\
--Touch their lips and twiddle their tresses. 

(The dance had little hold \\
On husbandeyes wine-darkened, \\
Garden-gained, \& knowing well the nature \\
Of fermented fruit: Still, \\
Imagination burnished, \\
'Liding all the effort burnt \\
In tactics and confusion.)

Our chatathon, with frontseat tickets: \\
Cars pulled up unloading friends \\
And leaving, loaded up on lovers; \\
Others coupled on the concrete, \\
Some third wheel spun feigned absence, \\
Privvy to some ancient cycle: \\
Hot-girl summer; cuffing season.

--So close, so far, from Camp Elís \\
--A sunken floodplain, skeet release. % skeet = sweet + skeeter

Unreal City--Crýptic aérosol álphabet-- \\
Climbing past the pichação, its \\
Pretty pieces--Some small-minded up to heaven.

Afterwards, well. I go home, and smoke on the street and give butt to a beggar. I drink a yoghurt and watch a guy go crazy, just screaming drunk in another man's face. Spot someone squat, and shit on the pavement and kick it, like a dog. I've been going round, photographing the inside of trash cans; I've been interested in a neighborhood's waste, in its disposal systems, in its use of clear \& colored bags.

And I find O'Hara's ``Personism''--surfing, back in bed, to fill the empty pre-dawn. Looking for voices; still not liking the sound of my speech, \& mimicking music of others.

And because all these foreign placenames make me think of Frank, \\
Who loved to write his lines like letters, \\
I settle it then \& there, to write this poem to \\
Ariel, my brother, Cris, my boyhood self.