Psychedelic wobble, \\
Creek-cut corso through the \\
Jungle-lush \& tangle.

Then passed vicious dogs \\
I fended with a walking stick \\
Toward cachoeiras, catch ya later; \\
Up through red clay beaten \\
Into stepwell, sculpted by a \\
Thousand hardened heels' press \& \\
Thousand soft'ning rains.

\secdiv

--Be Still A Moment Childe-- \\
--There are lessons still to learn here.\footnote{Heronbore, ``Vegetable Empire'': ``Wait. Stay a while. There is more to be explored here. / Acceptance at this point creates a lull. Wait here.''}--

Lessons like: No architect--\\
Just compounding gesture-- \\
Can discretize a slope so smooth, a \\
Thousand selfish steps, \\
The flat spots picked for pounding; \\
Discretize a smooth slope into righteous angles.

Then cut past termites' orange adobe, \\
Old adobe, domed adobe, \\
Roman concrete secret, \\
Sunbaked \& stigmergic.

Shaggy growth \\
on under- \\
groove of roots \\
in shaded grove.

The breeze keeps trees in arcs of temporary tension. \\
The hawk-cry carries menaces where the prey-lings chirpings cheer us, \\
Little watchlings, watch our power, spill our beans: \\
Time current-carves, and stacks in stone. \\
Accumulates and then erodes \\
As walkers of a trail lay the trail down again; \\
And all the pretty stones on paths are plucked \& pocketed.

\secdiv

Flipflops like a Roman sandle \\
Oiseaux exotiques and \\
Sunbaked brick \& vibora in slitherbrushes \\
Crossing such a path was \\
Dudley, young fool Dudley, heel-bitten.\footnote{\textit{Lodge 49}} \\

Getting lost in small-scope stories \\
Getting lost in grandlarge stories \\
All anxieties are here, in \\
Reconciling disparate, the \\ 
Gap, in checking correspondence, \\
Keeping up with inbox.

In the frame and interruption \\
Jagged lightning boltbreak from \\
Satchitananda. \\
Wont to stay forever in a single second, but \\
Distances demand traverse, connections made, \& anyway \\
Heaven like all company doth spoil in three days,
Kairosclerotic, so will you \\
Find my path? My dear pathfinder. \\
Art like any art, an \\
Art intending \& attending-- \\
Quiet now, and notice here: \\
What patterns hast thou seenest ere? \\
A virgil in the forest dear.

\secdiv

``My God! The Source!'' you cried from high, \\
Shouting Robertin Irwin lines on \\
Optics over roar of falls, the \\
New ideas slow-swimming into focus, \\
Watching white rush carving, \\
Black rock shaping \\
``Structuring structure, which is structured \\
By the flowing force it structures.''

Swingvines, far from latticework of leftbehind city. \\
I say: \\
``In other words, everything changes everything else!'' \\
Which is half true, but feels great in the moment to say, \\
Really strong and powerful, thinking how \\
These impressions on the senses etch in memory, \\
Informing here the words I'm forming \\
Channeling a groove in minds of \\
Readers--Yours--

% No real transition into the next section ("No Simple Trick")
% Which perhaps needs moving anyway