% The poet's partner, Anteros, flies to join him in Brazil as part of a 
% research trip around Latinate countries, looking for a home.

% The poet heads to the coast with Cris & Anteros.
% They eat açai and swim in a pool under a waterfall.
% The poet takes early-morning walks alone & refuses to feel lonely.

% ExSci status: Soaring, gilded, heavenly.

--As the laundry women'd say-- \\
--Amante especial, oi vei-- 

At the service counters, clients \\
Tracking comedramas of their catenary \\
Clientele (For if one must thus pay attendance, \\ 
Ought enjoy the bought performance.)\footnote{And if one plans to buy a pair of pants, one \\
Ought as well to get them tight, so anyone'll bed you. --O'Hara, ``Personism''}

Anteros had flown down, hence the chatter: \\
We were in the process \\
Of deciding where to live, \\
And how. A course of trips to tell: \\
Fróm New Wórld tó the Old; \\
From yesteryear's province now tomorrow's core; \\
We wanted a Latinate language; \\
Wanted a neutral passport, in event of war. \\
Two to three dozen inches of rain; \\
Warmish weather year-round and a little land, \\
To call our Kingdom; \\
Nonstop flights to Newywark, for our \\
Short-run social re-up missions.

It was hard, projecting yourself \\
Into some imagined future-- \\
Guessing at the form you'd take on \\
Fifteen years and half a million bucks. \\
The more we saw, the more it seemed arbitrary, \\
Where we settled. Spreadsheets helped \\ 
To take the Romance out of Romance language.

O My Goldenfleece Girl; on your last day \\
We drove to Camburi, down the coast-- \\
I was virgin when it came to açai, you know, \\
Me first time really getting it, \\
And the gilded stray who limped, before we \\ 
Lept from solid rocks to flowing pool below and \\
Used the roots like ropeswing in the \\
Magic hour's aur'ate spray.

Of course we all thought of Tarzan-- \\
We'd all seen the movie, hadn't we?-- \\
And the mere mention of tu/can lent a scent \\ % Currently trying to pun on "you can" but IDK if it works
And charged the scene of our descent with póssibílitý.

Ô Mãe d'Água-- \\
Early morning rising singing \\
Walking sandy sickle, bullion shore, \\
Along the veined \& fatty sea \& \\
Feeling young, eternal perched on \\ 
Billion-year-old boulders, under ancient skies \& all the \\
Tidelines marked by barnacle, \& \\
Not me crying, ``Not this time!'' \\
To loneliness, who many times before had tried \\
To wash upon these rocks of mine.