\end{verse}

Diane--

February 27th, 7:45 PM or nearly 20:00. I've never seen so many trees in my life. 

Making my own coffee in the house out here. My host is an exmilitary colonel, 5' 4'' and distinctly indigenous, who for years lived among the Yanomami. (Ya--No--Mami.) He showed me his collection of bows and blow darts. They wear bromeliads, made from feathers, upon their arms, as if their arms were tree-trunks. 

Somehow they've gotten it into their heads I'm a writer. The Colonel asks me how many books I've written. He says, Only children read books here. Or rather, this is my interpretation; we have been communicating by way of broken pidgin Latin. 

Diane--

10:27 AM. Coffee on the kettle. My hosts have offered me a ride into Rio Grande, where I'll catch the train. The Colonel offered but if I wonder if the Señorita is the brains behind the operations--he may be excommando but she's the family strategist. Was it this easy for blue-eyed bearded Cortez to conquer the hearts of the Mexico? Or plume-capped Pizarro, further south? Poor huéspedes, to slay a host. 

The Señorita is a sweet woman, and she is also a mother, who loves her family dearly. Which is what worries me.

Diane--

1:33 PM. I have arrived in Estação Luz and will be catching a car to Jaguaribe. Sorry to hear about the cold. Hoping it's mere coincidence, what with the MEO, if only to assuage my guilt. But cats will keep you up all night—could've worsened sinus irritation.

Sunday night sleeper works fine with me. I, too, have had a helluva couple days \& could use the R\&R. Turns out it's hard work, LARPing as Romantic poet--at least if you come to it with something approaching Protestant ethic. Still, the trip was beyond words--I leave satisfied that I have gotten in and out cleanly

\begin{verse}
