% The poet travels to Rio de Janeiro for Carnival.
% He sits on the beach, observes the wildlife, and watches 
% a parade at the Sambodrome. The culture of flesh appears
% to revolt him.

--By day the polycoughers goblinmode-- \\
--From chevar, moto, glassy couchsurf.-- 

Or in January's city \\
Plastic surgeon pecs \\
Cosmetic sex \& preening \\
Booze brigade of fairyqueens \\
Descending underground.

Cris provides a live translation \\
As the train arrives in station:

--I'd love to pour oil all over your hide-- \\
--Why? To watch your boomboom slide.--

It scanned \& rhymed in Portuguese, of course \\
And echoed loudly like an anthem \\
In the tunnels, others joined in. 

Swear I've seen this scene before, perhaps \\
In some old Flemish painting: \\
Bruegel, Pieter the Elder, maybe. \\

\secdiv

Portal promises of paperback: \\
Thin words in this the year our lord, \\
Omegaverse, romantasy; and meaify the \\
Cross-hatch formed by rival currents.

Shifting gaze past Sugarloaf, \\
The shaggy loafing lovers, \\
Sharing sodas, lemon máte, seasoned meat \\
It's mating season, meet'n'greet in pidgin Latin. \\
While blue ships on blue horizon \\
Drive toward trucks to trudge loads inland.

--Under pitched sunbrellas:-- \\
--Picturesque young Cinderellas.--

Palm fronds do the hula while I'm flayed \& sizzled. \\
Towel-talking, loving language. \\
Which were perfect popsongs of a poem? Like \\
Frankie's ``Coke''--and which were perfect poems of popsongs? \\
Cohen's ``Suzy',' Joni's ``ka{\textsci}.o{\textupsilon}t''-- \\
All of them, plus ``Prufrock,'' love-ode. \\

\secdiv

Forever \& always in the age of glass \\
The age of windowshopping \\
Love, \& sex, in crackt arcades \\
A tablet trance to faraway beach \\
In this, our Touring Twenties. \\

Bossa in the old cantina \\
Cold beer lifting heat like evening \\
Breeze, \& kiddies craning cameras \\
Skin as brown as betel-nuts, and \\
Airy hymns from half-caught eras.

\secdiv

Carne-levare: bid farewell to flesh \\
A Roman remnant diasporic \\
Fatty Tuesday excess 'fore the lean-mean Wednesday Lent \\
But here the party never ends.

Evening at the Sambodromo: \\
From our chairs we chatted \\
Charted floats slowprogress \\
Chanting crowd incanting chorus \\
Lowd \& rowdy \\
Cheering stars who flaunt \& shake \& \\
Flow to samba's rhythmic current \\
Down the corso's \\
Shoreline, costumed cosplay torsos \\
Fest of fat and fleshy skin and \\
Winkless sleep slowsetting in, \\
The Sun King and his sinking Queen \\
Their crowns of rays \\
Their solar spokes arrayed \\
In radiating angle \\
Tended by a bend of angels \\
Featherwingèd, free of fetters \\
Wringing salt from festive tatters \\
Fire-singed and filing, singing \\
(Not trivial in tropic weathers) \\
Wending toward the barricades, the \\
Great brigades of cosplay tribes, the \\
Front-row seats secured by bribes.

\secdiv

And what they sang?

--O céu vai clarear \\
Iluminar a zona oeste da cidade \\
E Deus vai desfilar \\
Pra ver o mago recriar a Mocidade \\

A luz que nos chega da estrela primeira \\
Nascida do pó no Cruzeiro do Sul \\
Do plasma divino das mãos carpinteiras \\
Ressurge candeia no breu nesse azul \\
Será que o limbo da imaginação \\
Perverte a inteligência \\
O homem com sua ambição \\
Desconhece a razão desatina a Ciência \\
Será que há de ter carnaval, sem minha cadência? \\
Com alas em tom digital \\
No fim da existência \\
Me diz afinal quem há de arcar com as consequências?

Se a Mocidade sonhar \\
No infinito escrever \\
Versos a luz do luar, deixa! \\
Quando o futuro voltar \\
A juventude vai crer \\
Que toda estrela pode renascer

O verde adoecido da esperança \\
Ofega sobre o leito da cobiça \\
Quem vive pelo preço da cobrança \\
Derrama sua lágrima postiça \\
Fogo matando a floresta \\
Bicho morrendo no cio \\
Febre no pouco que resta \\
Secam as águas do rio \\
E a vida vai vivendo por um fio \\
Naveguei \\
No afã de me encontrar eu me emocionei \\
Lembrei da corda bamba que atravessei \\
São tantas as viradas desta vida \\
A mão que faz a bomba se arrepende \\
Faz o samba e aprende \\
A se entregar de corpo e alma na avenida.