We bid farewell to flesh and set out towards some \\
Beautiful Horizons, in the General Mines. \\

Padkos for the journey; \\
Morning spent in Burle's garden: \\
Sung to Jagger's ictus-accent, \\
Every beat a stress:

--Lit/tle In/di/an fig,-- \\
--Where is your ownnnn skin?--

And near a chapel perilous, on sugarcane plantation hill, \\
O thousand-trunkèd tree all webbed \& curtained \\
By your symbiotes, your rounded staghorn scales, browning 'bove \\
Bromeliads, which brace \& cup your branches, catching rain.

Learn of leite politics while driving \\
Through the lactate kingdom of a lesser time, a \\
State a stage in process, forming, \\
History informing, never blank-start always twisting \\
Writhing, snaking; breaking down the self \\
To build another up:

% This isn't very clear, and never explicitly uses the 'cafe come leite politics' phrase that ties it in w/ breakfast orders
"Curral, cabresto, comitiva \\
Tropa, tronco, guided griddd \\
Eito'n'lavoura, grooved carreira in alignment \\
Oscillating oligarchs in \\
Yin'n Yang collapsing \\
Milk from young República, \& \\
Frothed en gran fazenda..."

By lateish afternoon we'd reached \\
Hill country, pastureland where \\
Shimmerwaves wind-racing cross the faces, \\
Silver quickflow in the fore as

Pearl-linèd clouds enormous, \\
Currentpulled with all the rest, peek Godly light, \\
While we atop indifferent engine, \\
Bubbleglass enveloped barely sense it. \\
Cris puts in his upper-decky soaring \\
Carving in through shadowpatch and piebalds, \\
Unfenced ungulates, us setting out to Cuntry \\
from the Seedy, Os Mutantes, male movement.

--And underneath the hanging vines-- \\
--A chessboard, gridded black \& white \&-- \\
--Inlaid into concrete table.--

Then drove from old Petrópolis, where some long-lost writer lived \& died \& got a street named after him. \\
We play Genesis to Exodus, \& skip around Ecclesiastical to Solomon, on Bluetooth speakers; \& I asked: \\
How far is proverb anyway, from catchy everyday cliché? \\
(Well, Cris said, a chiliad. We left it there.)

The Beats wrote odes to Menfriends, \\
Breaking from tradition-- \\
Troubadors and Bedouins--Instead-- \\
Sung ballads of heroic age to \\
Celebrate the courage of their boys, in War with the Machine.

And of merenness at night bejewelled \\
By other steersmen, ancient world. \\
Hard to not see God herein the pasture.\footnote{Secession from modernity. Regression to an earthworm life among midevil peasants, types the Heron, bored.}