Near ides, ride SPR to outskirts, \\
Catch a bus: Paranapiacaba. \\
Railtown of long-set sun, \\
In canyon where the mountains break \\
So fog advances with the trains \\
And pulls into the station.

But on sunny days I find, \\
A higher kind of hedonism: \\
Bougainvillea, staging site for my transcendence. \\
Peak at plastitropic lower canopy through lover shutters. \\
Smile warm to traduttore traditore, \\
Hostess of her hometown: \\
Tories sleeping in the kitchen.
(There's a law against that.) \\
So smooth she is in service \\
Seen our kind a hundred times before and will, again-- \\
We glide up to the bar where she's \\
Presiding over leisure center, \\ 
Move our mouths, per-form for nativetongue appraisal, \\
Try not to offender her.

In the yard os pássaros pause \& pulse-perch, \\
Branch to phototropic branch \\
And in the grassblades, guava windfall, \\
rapid-gathered by the ants.

That night we many write in Father-ink that bleeds, among a \\
Graveyard: matchsticks, blackened spliff \\
These tubes with charcoal tips, with \\
Ends that burn \& ends that do the burning.

Distant train loops 5\textsuperscript{th}s in \sfrac{6}{8}\ \\
On a swivel like an owl's neck the \\
Camera tracks me as I move, \\
Naked between bed \& bath \& \\
Light a cigarette--

Or write, which must be why she said-- \\
--Ele é um escritor-- \\
How now can I act, without performing for her gaze? \\
Tlamatini, man of mirrors. \\
(More like topiera.) \\
\hfill mule

All is long, is long, is long. \\
All is long-- \\

Every thing talks back, when we're alive \\
(A heron told me that.)

Red fruit in the sun-faced green of high-branched tree-- \\
Morning's energetic harvest now announced by feathered flutes, and \\
Green sunpanelled flapping fans that move within the Planet's currents: \\
Breeze that passes through the guavas, carries chatting prattle of the parrots, whistling \\
“Oh que bueeeeeno” and “I'm talking to-chyou.”

And through the branches Heavenrays--tempted in my own sick way to say— \\
Brigado to the old Brigades whose cutting brought me here today. 

Can hear their echo of past presence. \\
Quiet forms, machete wháck! \\
Of breakerpath, in \\
Fallenstem \& structure-- \\
State of the Green Tower, in the \\
Age of Metal, singing, \\
--Chattanooga answers / And your ma'am in Tennessee.-- 

And the mood changes as the goldleaf fades. \\
Cloudcover which is at first relief now will not lift. \\
Cricket trill announcing us the end of little world.

Invading ginger enters at the clearcut, \\
Roadcut, in the slash-mowed marginals, \\
Along the barren no man's rock'n'gravel we call road. 

Which clearing flows through living mesh, \& \\
Lets me pass, \& \\
Contact's always Contact with communities whom Contact's altered.

\secdiv

Noon, high noon. \\
Baked into prehistory-- \\
Stonesmelted--\\ 
Don humming “Well, you wanna get enough sun / but not too much.” 

Starting to get to a point where triunesweat unzippers. \\
Traveling back to High Noon: to a moment of \\
Maximum intensity, when shadows' shields at their slightest. 

The moment now of max'mal heat, \\
and pressurewaves whose radiation warpeth man, \\
and burns him up or out. 

Watch flutterfly, and unleaving, ants \\
are bringing off the body of a hard-shelled giant, \\
from the shelledland to their tunnels. 

Radiation warping man, he sees the Raptor in the Turkey \\
Enough to make him paranoid, the sounds responding to his presence. 

Make it nearly back to town now, at the fringes half-reclaimed: \\
the Warhead windows where the bakery once stood. \\
Heatbeat down on unprotected skin, \\
``Brown as a betel-nut in the morning.''

Wrest controls back from Pleasure Center. \\
Get back to business at hand \\

--And I have lived the fates of foreign diets in a for'gn behavior.--

--A hunch: perhaps I've been infected; what I've given, also gotten.--