% \& it's Me, the Mockingbird \\
% Up at dawn with morning dove \\
% To learn the songs of valleys \& to \\
% Sing an alba to my love.

Says Crístobál, this region's known for \\
climbing, then corrects my accent: \\
``Meu nome é Cristóbal`` \\
I say, Fair enough but good luck iambs, \\
Other rhythms here resisting meter.

``Check the slicker'' he says, \\
But no palheiros. \\
When I ask for climbing handholds \\
What I get are handles: \\
Crimps \& jugs \& pockets \& rails, \\
In-cuts, slopers; slippy, chaussy, glassy. \\

Then he gives one of his infamous reports from the interior.

Remember: Back in Brooklyn, \\
Cris had drunken-staggered \\
(Twas a tipsybuzz at best; \\
This telling’s fond of its excess) \\

--All this money, what does it buy you? \\
--All are heavy, drugged up the wazoo.

For gain’o’grain they banner-band together

Like Liberman had felt, regreso \\
From thatchèd Filipino rooves \\
And breeze blocks \\
``My people full of lightness

--It was something like: A relaxation.
--It was something like: A lesson in negotiation.

Recall-- \\
(Proleptic analepsis) bite o' \\
Meatbeer breakfast, bar o' \\
Mushroom chocolate-- \\
Parque nauseous, weathered under bower, \\
Dozenmile walk, \\
Sip finnest rums on Thames \\
(All overproof) \& \\
Sideline goofing.

``Some folks are just like that--
Treasured by the Gods \& better \\
Off avoiding effort.'' \\
(Others in the darkness drill, \\
Chisel stone to timeless still.)

And me? \\
A screaming Carioc \\
Til dawn-- \\
The rain, the fortune's sons \\
The blueridged mountains, rolling \\
Rivers, smokehoarse \\
(Jeff had mimicked Satchmo) \\
Then, hungover, hair of \\
Most exquisite science: \\
Heronbeast--hysteric naked, \\
Raving nightsweat, bedwet-- \\
``Brotha!''

