--Grã Grayhouse, grow like grão \& upgrade.--

Chlorine cleansed us. \\
Toweled-off beneath sunshowers \\
Flew then past the Água Branca \\
Villa Country's block-long false-front's \\
Cowhide seats and leather saddles, \\
John Wayne photos, chandelier of purchased antlers. \\
Cris would not go in, or stop; \\
I toured the spot by satellite that night, saw
Aztec ravers, PLURgirls, pulled myself away \\
And prepped for 'piacaba: \\
Worked through poet podcast, \\
LARP takes preparation, \& I hoped to LARP \\
Like All Romantic Poets, long-past, \\
Just to see what it was like, I guess, \\
And if the form might suit me. \\
With some tailoring, I guessed.

And learned, for instance, Hopkins \\
Born to one marine insurer \\
Safekept 'gainst the wreck of craft. \\
A Catholic Manley haunted by a woman's resurrection: \\
Winifred whose wellspring sprung up where she was beheaded.

--Willowrun: \\
--The downward flow allows for an upward growing. \\

Byron, Shelley, Keats-- \\
The peacock, Theban poets-- \\
Boating with the boys \\
While Mary watches \\
Says Pistelli on the speakers \\
These Romantics not romantic \\
Much beyond the Year of Cotton \\
Harriet? Was not invited \\
Riverdrowned, a Virgin's pebbles--\footnote{41.03.28} \\
Bob \& Joni's kind of freedom.

The plan to walk, drink tea \& mumble in the wood, \\
And sing to birds, and squeak a caller's zinc on birch, \\
And make strange sounds meant for myself, \\
And treat the voice as instrument, and words then not as \\
Discrete objects but a blended space-- \\
Which was not dissimilar to the brass instruments of my youth.

And insofar as the Beats were, of course, a new Romantic, \\
But also in the Wakean sense of harmony, \\
Where each word is really three or four or five words spliced-- \\
All part of my new theory of practice I call vox libre, \\
Which I invented after lunch, \\
Or really in the House of the Owls, Rome, \\
And which only a few people know about, \\
And less understand.

Dry the hands on the dishrag, sigh lightly\\
Will have to skip back I guess, \\
In increments of ten. \\
Frost, he didn't wanna be caviar for the crowd \\
He wanted to write for all sorts and kinds \\
Maybe for the money, no one really knows \\
He was just as clever as Pound, \\
Just as wellread as Pound-- \\
Or so friends say. \\
Even knew more Latin \\
But he found his layers in a tone of voice \\
Instead of learnèd reference.

New England's pasture poet-- \\
A means to butter parsnips. \\
A labor of the hand much like \\
The rhythm of a scythe as it swishes the meadow:
Softspoken, cutting down ranks. I'm on a digression but how do I get used to \\
The everyday violence of gardening, is what I'm always asking. Because there's something fascist (no?) in pruning branches, weeding roots. Well.

Another ten, the double tap: \\
Poetry was performance. \\
Poets were athletes, men of prowess. \\
He studied the rhythm of American talk \\
So did Ginsberg. So did Gaddis. \\
O'Hara certainly \\
He listened to their musicality \\
He tried to imagine how they'd sound behind a door, \\
Indistinct and muffled.

He read Emerson. \\
He talked in contraries. \\
Who didn't? \\
Whitman played without a net. \\
He'd never owned a desk. \\
Who needs one? \\

His reading was lowercase catholic. \\
His American shoes gave him away. \\
Pound was all silence with eagerness. \\
His instinct said to stay away from gangs. \\
His mother ran a school in Lawrence. \\
He taught classes, when he felt like spring. 

He leafed through anthologies. \\
Pound had showed him Bohemia, jiujitsu \\
Flipped him, heels and head, after dinner in some cafe \\
Frost was just as strong; he hadn't been ready \\
Read more Greek than Pound, he reckoned \\
And busted Pound right outta jail \\
Settled it with the Attorney General, just like that \\
That's what you can do, when you're famous \\
When you're poet for the lawyers, and not just poets.

He reckoned his place among infinities \\
Didn't we all? \\
He went his own way \\
Inspired Sinatra to write a song. \\
Who are we kidding? \\
Sinatra didn't write songs. \\
But I will. \\
Don't we all, these days? \\
Not really. \\
I assembled fragments. \\
Didn't we all? \\
The lecture was very persuasive. \\
Afterward, he renounced the concept of \\
Intellectual property, \\
And burned with shame \\
For his once love of indie rock.