% Should find a way to connect St Winifreds Well to Frost's wellcurb

--Grã Grayhouse, grow like grão \& upgrade.--

Chlorine cleansed us. \\
Toweled-off to sunshowers, \\
Mechanized carriage past Água Branca, \\
Villa Country's block of falsefront bars \\
With cowhide seats \& leather saddles, \\
Chandeliers of purchased antlers. \\
Cris didn't register the appeal; \\ % Nothing line
I toured the spot by satellite that night, \\
And prepped for 'piacaba, playing out a poetpodcast \\ 
Taking notes--I swore it'd be my best performance-- \\ % Eh
Hoped to LARP: Like All Romantic Poets, long-past \\
(``Dead'' in sense but somehow speaking) \\ % Meh
To see what it was like, I guess, \\
(I knew a girl from Barnard loved her Keats above the rest.) \\ 
And if the form might suit me with some tailoring, I guessed. % Does this earn its keep?

And learned, for instance, Hopkins was born to a marine insurer, \\
Who safekept lords 'gainst the wreck of their craft, \\
But could not spare a crew or captain.

A Catholic, Manley--haunted by a woman's resurrection: \\
Winifred, whose wellspring sprung up where beheaded.

(Willowrun: A downward flow allows an upward growing \\
Long the bank of fallow fields, waiting for their sowing.)

Byron, Shelley, Polidori: Peacocks, Theban poets-- \\
Boating with the boys while Mary watches-- \\
This is what I learn, for instance, from Pistelli on the speakers-- \\
These Romantics not romantic \\
Much beyond the Year of Cotton. \\
Harriet? Was not invited-- \\
Riverdrowned, a Virgin's pebbles--\footnote{41.03.28} \\
Godwin's wishful thinking tested; \\
Bob \& Joni's offroad freedom \\
Slave to courtship, Hudson's Stetson...\footnote{Rock's Rex, \textit{Pillow Talk}}

Long digression--The plan was-- \\
To walk, drink tea \& mumble in the wood, \\
And sing to birds, \& squeak a caller's zinc on birch, \\
And make strange sounds meant for myself, \\
And treat the voice as instrument, as men before had done \\
But mostly tried \& failed \\
(Mine would be another failure) \\
To make of type a moltenmetal-- \\
Blended space a better place-- \\
Which was not dissimilar \\
To the brass instruments \\
Of my youth.

For how the fretless trombone flummoxed. \\
Yet a student's slide is taped, and \\
All its open space is snapped to \\
Gridded notes correct, implying in their midst an error. \\
I was always finding my positions, \\
To keep in tune with teammates: \\
Metal merely modulates what's buzzing in the mouth.

And insofar as brassy Beats were--must it be said?-- \\
A new Romantic. \\
But also in the Wakean sense of harmony, \\
Where each word is really three or four or five words spliced-- \\
Were all part of my new theory of practice, which I called vox libre, \\
Its manifesto penned at lunch, \\
As Frank did it, \\
Or really in the House of the Owls, Rome \\
And developed in Trattoria Luzzi.

And which only a few people know about, \\
And less understand.

--Snap from drift \& dry the hands on dishrag-- \\
--Sigh lightly-- 
--Have to skip again I guess--
--Tapping through time, increments of ten.--

Keats, at least, was protean and modest, \\
Like the song of starlings, cuppèd self to carry world. \\
(Wordsworth, though, an egoist--Pistelli here a moralist-- \\
His poets not just wordsmiths much as mimicked modelled consciousness.)

--What're you looking at, me? Shiit.-- \\
--And why'd you say the subtle thing out loud?--

Frost? He didn't wanna be caviar for the crowd. \\
He wanted to write for all kinds-- \\
Maybe for the money, no one really knows. \\
He was just as clever as Pound, \\
Just as wellread as Pound-- \\
Knew more Latin--So his friends say \\
But he sought Quality in tonal tenor \\
Rather than learnèd reference.

New England's pasture poet: \\
It was a means to butter parsnips. \\
A labor of the hand much like the rhythm of a scythe, as it swishes the meadow: \\
Softspoken, cutting down ranks. I'm on a digression but how do I get used to \\
The everyday violence of gardening, is what I'm always asking. Because there's something fascist (no?) in pruning branches, weeding roots. Well. I've gotten away from plot, and will the editor kindly leave these?

New leaf; another ten; the doubletap to learn \\
That poetry was performance--Poets athletes, men of prowess. \\
(Humble men, these poets.) \\
And that Robert studied talky rhythms \\
(So did Ginsberg. So did Gaddis.) \\
Frankie surely; Bobby-- \\
Listened to their music, tried to magine how they'd sound through walls, \\
Freed from con or denotation, muffled-- \\
Almost molten--out of all distinction.

Pound had showed him Bohemia, jiujitsu \\
Flipped him, heels and head, after dinner in some cafe \\
Frost was just as strong; he hadn't been ready \\
Read more Greek than Pound, he reckoned \\
And busted Pound right outta jail \\
Settled it with the Attorney General, just like that \\
That's what you get, when you're famous \\
When you're poet for the lawyers, and not just poets.

Frost, he leafed through anthologies. \\
His reading was lowercase catholic. \\
His American shoes gave him away. \\
Pound was all silence with eagerness. \\
His instinct said to stay away from gangs. \\
His mother ran a school in Lawrence. \\
Let him run some classes \\
\qquad when he felt like spring.

One last wetfingered tap \& it's time to get going. \\
Taptap. Tatatap. \\
He'd read Emerson. \\
He talked in contraries. \\
Who didn't? \\
Whitman played without a net. \\
He'd never owned a desk. \\
Who needs one?

He reckoned his place among infinities \\
Didn't we all? \\
He went his own way \\
Inspired Sinatra to write a song. \\
Who are we kidding? \\
Sinatra didn't write his songs, but I will. \\
Don't we all, these days? \\
No. More assembling fragments. \\
Didn't we all these days? \\
No. Immemoried.

The lecture was very persuasive. \\
Afterward, hand in hand with his high school sweetheart, \\
He renounced the concept of intellectual property, \\
And burned with shame \\
For his love of indie rock.