% The gang drive home from Camburi.
% Anteros is dropped off at the airport.
% The poet rearranges the flat and writes for three days,
% Lost almost in a sort of underworld.
% Then he emerges ecstatic.

% ExSci status: Down & up again.

And driving long the skyway, \\
When the tunnel opened up on such big blue \\
We played a Bushy ``Big Sky''--Kate's--\& sang along, all \\
Shouldershaking-- \\
Lost in flows, we nearly drove right off the ledge. 

And then dropped at the airport poor Anteros-- \\
Actually, she took a car. \\
After she was gone I rearranged the dining room. \\
Turned the TV on Megachurch \& Christian infomercial. \\
And I went to work for many hours, \\
In the darkness, under HVAC-hum, \\
\& neither ate nor left until the sun rose \\
On the third of days...

Then so giddy, kicking, skipping on the sidewalk, \\
Like San Xóbal, singing \\
\qquad Mama, Mama, Mama \\
\qquad Don't take my kodachrome away.

My mustache died a perma-purple, sipping those elixirs. \\
Such good times, I'd stumble downstairs past the doorguard \\
Find a table on the sidewalk, wait to say \\
The same words every time, a joy just getting right: \\
--Bonjia, todovem. Dois ovos, sim, meshidos-- \\
--E cafe com leite—e um suco com laranja, por favor--

And most times getting what I'd wanted, hoped and tried for. \\
Well, I won't trouble you with a theory of language \\
But it felt like singing, and it felt like magic. 

And Cris? We were to spend a month together. \\
He'd been learning to read the city-- \\
Blockquote, concrete syntax, gridded layout. \\
Taking the same walk everyday \& seeing what happened-- \\
How the parts fit--Perec counting cars-- \\
He was writing about Parisian corn carts: \\
About mass \& readymade units adapted \\
Into custom forms, over years and generations. \\
He was interested in lightweight/portable/nomadic architecture. \\
In minimum-viable rigs. \\
The natural, everyday look of lighter \\
Coverage could not fool him. \\
He always noticed people's shoes; \\
I mentioned Frost, abroad. \\
An exlover in Janeiro-- \\
\qquad ``That's the thing about Cris; he's always looking.'' \\
She said he was a gringo, for the way he wore his fannypack. \\
\qquad (Insufficiently guarded). \\
She said he was a gringo, for translating ``polvinho'' to \\
Tapioca dust. \\
