\textgreater{} be me \\
\textgreater{} be backpack lad \\
\textgreater{} always carry on, never check \\
\textgreater{} gate lady says i have to check it anyway.  \\
\textgreater{} annoyed but whatever.jpeg \\
\textgreater{} go through security. no one asks for id.  \\
\textgreater{} security theater.exe \\
\textgreater{} get to gate. wait around. acquire mcds. \\
\textgreater{} mfw m\&m flurry. \\
\textgreater{} maybe flying not so bad. \\
\textgreater{} my group is called. go up to show ticket. \\
\textgreater{} same lady. \\
\textgreater{} ``passport please'' \\
\textgreater{} look for passport.  \\
\textgreater{} ohshitohfuck \\
\textgreater{} passport is in checked bag. \\
\textgreater{} give her license instead. \\
\textgreater{} ``no anon, must be passport.'' \\
\textgreater{} tell her what happened. \\
\textgreater{} sorry anon you cant board.  \\
\textgreater{} i see my bag outside sitting on tarmac waiting to be loaded. \\
\textgreater{} point. \\
\textgreater{} doesn't matter \\
\textgreater{} vestguy says he can get it off tarmac, no problem \\
\textgreater{} gate lady says no, anon will have to learn his lesson. \\
\textgreater{} \textgreater{} learn his lesson \\
\textgreater{} says to catch the next flight in a couple hours. \\
\textgreater{} sends me back through security.   \\
\textgreater{} get in queue to speak to airline \\
\textgreater{} ``sorry anon no flights til tomorrow.'' \\
\textgreater{} ``also you will have to pay full ticket price.'' \\
\textgreater{} silent seething. \\
\textgreater{} sleep on airport floor. eat stale honeybun from vending.  \\
\textgreater{} start reading unabomber wiki \\
\textgreater{} maybe he has a point.