And there are no Faces anymore, the World is Faceless. \\
Instead we are a system of other signs, \\
Which speak to our position, assets, raising-- \\
All but emotion-- \\
And are become in turn our masks, \\
And not the feeling under them.

What cruel karma now, enacting crudekliche of city cynic, \\
Manure in me boot-treads for going back to ``Country,'' \\
Raymond Williams face; say ``I am disappoint.'' \\
A village yokel, yuh, for thinking city folk'll like ye.

Oh but how gay \& light is Frankie! \\
Polymorphously perverse. He lurved the city. \\
He loaved the city. He luffed it. He had lovers all over it.

When did I love the city? When I was in love, I guess. \\
Or when I dreamed of what it worked, when work that way did not.

Our cabbie spoke six words of Enlish, one of them when we told her where we'd come from: \\
--Beyoooteefull! she cried; not words I'd usually use \\
To describe the Concrete Wilds.

Mayhaps I'll write to Gershwin's reed, I said; \\
Sensitivity was the heart of it. \\
What I'd lost and what I needed.

The piazza was packed with twenty-somethings. \\
I sung, \\
--We all know you're hard cuz we've all seen your leather. \\
--We all know you're soft cuz we've all seen your sweatpants.

Fascist inbreath. \\
Acquiescent out while \\
Polystyrene \\
Poly sirens \\
Ply their styles, \\
Renegotiate their terms \\
Of social presence with a crimson smile.

The girls are Old Masters of brush \& blush. Dark foundations through  lightdusted overcoat. Now the perfume bottles. Whole carriage smell of bouquet. I felt myself traversing the curve of a Yerkes-Dodson while she spoke.

Ben--It's said in every world walks the perfect being once... Roman candles are his hautboys. But does he, or is this a wished simplicity? Do we still believe that Beauty stands sure proxy, costly signal of our Quality? Or is much beauty treacherous, a lure from deepsea deadly fish?