\qquad Boi Na Linha, Ferrovia \\
\qquad Gunning Westward Todavia-- \\
\qquad Fifty Million-- \\
\qquad Wiped To Make A Window Clearer.

Stroll through aging downtown, \\
Triple flagpole, \\
City state \& country, Russian doll \& \\
Apple blossoms shake \& breeze-blown \\
Past a litup stagecoach, old \\
Wells Fargo animation in electric \\
Bulbs \& all the childless people, walking dogs \\
Who squat \& shit \\
The shit picked up in plastic bags, \\
Slipped over palms, \& \\
Leaving pavement smear \& grass-stuck \\
Where we wish to lie in sun--

And here--the Polis \\
Plaza, ded. to soldiers of the \\
Greatest Generation, 'for a \\
Boom \& bust; the \\
Patron's names in carved mosaic \\
Fallen petals--white, \& wrinkledrying, \\
Fallen from the Source, a sort of \\
Fresh-snow sexfest, vines around the \\
Concrete columns, stringlight bulbs for \\
Blossoms hang in tangled trellis, \\
Racemes of wisteria-- \\
Ubiquitous-- \\
Is beauty's crown so \\
Weeping on the corner: Pompeii \\
Restaurant, wine \& terrace seating.

Nearer to the Nineteens, \\
Ornamental clock, its \\
Gilded follies' tolling tongues \\
Forever telling what we know \\
Already and with more precision, obsolete \&

Here is Holder's Country Inn-- \\
Colonial \& double-dormered, \\
White-trimmed brick; \& Here Los Altos \\
Masons, with their trees in matrix trellises, \\
\& here the Gothic letterhead, \\ 
of Old. Town. Crier.

And chiming churchbells pre-recorded, \\
Manage still to lend an air of \\
Stately Law on State Street \\
(Which, in fact, the street was named) \\
Of some small-town Americana \\
Known to us by filmset only.

Or pace the suburbs' droughtproof gardens: \\
Rows of aleonium, \\
Their rosettes spreading \\
From Canary Isles, or the \\
Zulu jade, or racemes-- \\
Glossy, porcelain, or glycine, \\
Chinese; smell of \\
Mármara, in Märe's dewy rose, with \\
Periwinkle flowers, \& \\
Egyptian treefigs pruned, their limb- \\
stumps tarred \& bald \& blackened healing-- \\
All these migrants 'mong the silver scrub,
\& old-man oaks of California. \\
Shedding splinter-hide sequoias, \\
Root-twist redwood to uprightness.

Her childhood home? \\
Hemmed in by ornamental cactus. \\
Security lights \& motion-activated cams. \\
But tonight we're magic, both of us are \\
Magic, as-of-yet uncaptured. She can speak to cats. 

Let us never turn into our parents, darling. \\
Let us, if we hem ourselves, hem ourselves with berried brush.