He was a plastic surgeon. \\
He had a key to a better life. \\
He had a key to all mythologies. \\
You were to acquire scars with pride of experience. \\
He had learned this in Crescent City, from an eyepatched Creole, \\ And abroad, in Deutschland-- \\
Where men wore saberscars like medals.

"The acquisition of a horrible scar [on these boys'] cheek had the same psychological effect as the eradication of the scars from the cheek of my [patients]... The magic was in the meaning..."\footnote{Or as Xobal would say, in his paraphrase of Fisherking: "Just because the mechanisms are biochemical, doesn't mean the root causes aren't social-psychologic." \& Doesn't this mean we still (\& always, already) live in a witchcraft world, with so many forms forgotten? So the New Romantics say.}

The Magic was in the Meaning, he said. \\
The knife was always the same; it cut the flesh; \\
The Secret was self-conception. \\
His method consisted of the Medical Art \\
Of Creative Mental Imaging. \\
He believed in new habits: of thought, \& action. \\
We all had an in-built impulse for success; \\
It had been put there by our Lord Creator. \\
The problem was a blockage in our circuits.

You--yes, you: \\
When'd we Cease to Understand the World? \\
Coleridge got bang from Banks's botanic net \\
Under barktoothed, twisted, silverbroken \\
Oak, so small, in star \& wind \& systm \\
Ev'ry point a center.

And How each Man should build his Home, \\
Childe I know not. 

--Oh Mr Know Nothing, at it again! \\
Brktoothed, silverbroken \\
Ev'ry point a center. Distant \\
Cayot--Set my coat on mounded \\
Earth \& cave-in citadel of insex, \\
Watch its hazy shape horizoned \\
In the dustkey grass of this \\
American savannah.

\secdiv

Wherein-- \\
I am permitted a meadow--\footnote{R. Duncan}

The Afternoon Sun inquires tactful: \\
Ought one be a vine or trellis? \\
Crystallatticed mineral, or braided fibermesh?

Which clutching roots to yank? \\
Which branches branch? \\
And which deserve to die or liquify \\
To harden, blacken, lose sensation.

Where ought my swerving reach, \\
In chasing \& predicting light? \\
How like my shape to history, like \\
Pollock's painting-dancing record-- \\
Smoking arc and splatter where piss put out the fire\footnote{Peggy Guggenheim's, if mem'ry serves.} \\

Ledger, log decision, indecision, stimulation-- \\
Flood and droughts, the path of \\
Sun, provisions in the soil; \\
Where an owl nested in Hawaiian eucalyptus. \\
(Deed I missed it, \\
Pensive with the roadcut's crickets.)

\secdiv

--Have you no time for Eternity, Childe?--

A family joins me at the banks;
Their Father is their Shepherd, \\
Singingsong to childflocke, \\
``Say byebye to the water, darling''\\
``Uh-oh! Watch your step, offset,'' \& \\
Then they're gone again.

Shybloom truebloom; \\
Brashbloom false. \\
Play of interpretation: \\
Guessing at myself \& others.

``Jus' retire from the ole worl \\
Under that suckling appling tree, \\
Oh boy.'' Shkychilde. \\ 
How to discern, thout disenchanting? \\
Open the billows. Let the air in. \\
To be someone you are proud of: Doublefaced, \\
Double-anchored, one might change \\
The act or change the feeling, \\
To bring in accord, \& Iam so dilemma'd: \\
Kick your shoes off, twiddle toes in \\
Kiddish grass, cold riverbed. \\
Every way I know of knowing is coming apart at its edges.

(They wonder if I'm becoming a habit.) \\
(I would never--I am never coming back.)

My ways are wild \& strange, forgive me. \\
What picture do you set yourself, O Mother Mia \\
Coming home from work to see'er.

COLD CALCULUS OF RELEVANCE. \\
If pattern makes a substance, action makes a man \\
And namèd purpose does not make an institution. \\
Xóbal's message was: Be better with your tools, \\
And mine: Be better with your words' manipulation. \\
Watch your subtle tonguestrokes as they sing out their persuasion.

A one-woman map, assembled by \\
Candlelit moodboard, byCollage of images \& drawncards \\
Patron saints \& constellations, \\
Stars chart course in divination. \\
To be everywhere at once: That is paralysis \\
And nothingness, in indecision, \\
Empowerment's a resource; cash in; \\
Shapes your inner planet shaped \& \\
Reasons to respect \& dis \& mind, \\
Enslave to bind \& sacrifice, \\
Or disregard \& violate; \\
Not times for self-fulfilling Grump-Grump, \\
He had a love for the game; \\
That was all you could say. \\
Sitting in the sun, on the occasion of \\
The death of a father, the birth of a son.

The hawks know \\
What is pre-negotiated \\
And what is sudden improv interruption \\ 
Day of note \& strange intrusion.

``Why the pattern?'' \\
Can't be answered, \\
Cept by reference to environs' \\
Everythingexceptness.

Say: Ten of them's not one of me, \\
And turn our love to killing spring. \\
Turn our loving killing magic, \\
Towards our ribbon sycthe, barbed wire \\
Baby basket. Solo hiker, \\
For a view of a creekside cutout, forcecarved: \\
See where dead roots brace \& bulwark shore \\
And mossy cover shortermundisturbed a \\
Dappled slowdegrading structure... 

Time to toughen up. \\
A musclepath so concretized \& consecrated. \\
No more sitting, waiting. \\
No more backup boyfriends. \\
Marriage bands with bound circumference \\
Symbolize self-limitation. \\
Compromise \& fitted to environs, \\
Which is just to say the social works \\
By shifting flows of power.

And Iam not the apex here, but krill, \\
Amongst the wealth of middle age, a scruffy cap \\
(I crumple their view; they crumple me) \\
All eyes on me now: Interrupt my thoughts, \\
Pollute my purest stream, \\
For I pollute their nature dreams.

Yes no timeouts, and nudity: \\
Still dress \& fashion; abstinence a \\
Vote \& even pause on XBox severs \\
Context, dulling, clearing cache with headrest.

To be respectable as a man first: \\
And not just as a sneaking, filching poet, \\
Laozyparadisalponder.

Or to live in weave: To live to weave, \\
And leave no other dressing. \\
Thoughts like this my slumb'ring mind \\
Find so warmcarressing.

And when all the small soil, that the roots have held, that hold the roots in turn, erode-- \\
And Trunk Tower topples, on its side, \\
It falls \& forms a Bridge across the water.

Would I be nothing as a man, yet write about it? \\
And if I'm nothing as a man, have I the right to tell about it? \\
When all the soil that held the soil that held the roots that held the soil--

In such rich irrigation, water-drunk to end \& rot in'em. \\
Undercut \& caving in, crumbles in the current.

So make a system--else enslaved by others'-- \\
Some reject, some emulate, the ways of Mothers.

One thing certain: \\ 
One cannot always be sundrunk. \\
One cannot always be pulling at punch. \\
For those who pay the bills become resentful \\
(Or do they? Or do they enjoy vicarious. \\
Or do they teeter tween the two, never sure \\
Whose flagellate or -ating.)

What Jack, he said of lumberjacks, is true \\
You learn about the man from how he splits a log, \\
But true as well of every act \& style-- \\
All strategy speaks through tactic, \\
And every work doth testify as \\
Verbs carve \& chisel nouns \&
All paths trailmake, as all \\
Perception to perceiver \\
All things correlate this way, in \\
Hard-to-peel layers.