``En 189 acuñaba Henri Beraldi el término pirineísmo. Bajo él se agrupaba a aquellos que tenían la resistencia de ascender por las montañas, la facultad de percibir, y la habilidad para transmitirlo a los demás.'' (Wall text, Veruela Monastery, Zaragoza.)

Broad Balboa, top a peak in \\
Panama, saw sea to shining sea, \& Me? \\
Grace to God for Southern Seas, \\
Horizons which approached, recede, so \\
Occident could still suffice \\
For those who Orientalize \\
As Barbars saw the Visigoths \\
And Moorish slavers praised blue eyes.

``Best thing to do is dig-- \\
One thing or place or man,'' \\
Til knowing more than any man about it \\
So said Olson, on committing, not so much \\
To form as to environ-- \\
He should know! Ningland poet; \\
Jim chose foggy Dublin-- \\
Who am I above it, Johnson?

\& Beatific doubling, "dig"-- \\
But I? In better moods dig everything, a problem-- \\
Better-known to Beats-- \\
Of too much sun \& too much stim. 

What's the answer, then, but study? \\
Smarter, harder--¿Porque no los dos?-- \\
And better sure but slower, patient, \\
Play along Pareto's front a frontier, \\
Find the tax-free, rentiered double-dutied wins. \\
Well Pound \& Olson, Prynne-- \\
Had things for stones now didn't they, \\
Sculpture, rockeology, and chiseled gemstonepoems \\
Or stacking layers, timely sediment, \& \\
Wood turned mineral by pressure, \\
Polished sequence shining. \\
Not like jamband Kerouac, who tossed it out \\
Diffuse and free.

Permanent poetics and its birdsong-- \\
What is beautiful, ephemeral, \\
What lasts, a leaden echo?

``This is the morning, after the dispersion, \\
\& the work of the morning is methodology: \\
how to use oneself \& on what. \\
That is my profession. \\
I am an archaeologist of morning.''

More said Olson, cern'ing thru accumulation, \\
Centuries of text-- \\
He loved the taste of soil, so he said \\
And who are we to suspect? \\
Zeke was gave the infinite, \& \\ 
LA healthdaze craving bentonite. \\
Olson hunted hardened clay for scratching; \\
Stored his psychedelics in an owl idol \\
--Fieldwork composing-- \\
Chewed on alien maiz, \& gathered rosette potsherds. \\
Put together fragments watching indigenies' sheepherds.

Ô Mãe d'Água.
If we are in the morning of man, \\
Then that is a time for questions of method. \\
Dawning, always dawning, downing, setting; ev'ry \\
Veil just a vantage so select positions wisely. \\
Rather than commit, exploiting \\
Onward go with our exploring: \\
Carnival to Lent to Easter, \\
Feast of Feasts in Feastly cycle. \\
Cross the Roman West in armchair, \\
Wordsworth's Alps \& Meister Darwin; \\
Banks' Tahiti, Byron's \textit{Childe}; \\
Time Tombs of Hyperion. \\
Goethe's \textit{Journey}; Cook, von Humboldt;
Brönte, Stevenson, \& Melville. \\
Or Carvajal, who blessed with final glance \\
At Amazon as civic wonder, squandered handsome, \\ 
Caught up anxious in some future prison, \\
Couldn't soar with kayak orchestras, \\
Or justify his sight with reason.

There is no time, these days, they say, \\
To drink the blood of Christ \\
(There is no other time) \\
Nor take the waters \\
Cannot even taste our sweat. \\
To not be like that Carvajal--is any nobler promise set? \\
(Or Corpsey. Kid is showing promise.)

And too reporting (after Johnson) with  \\
An eye to study men \& manners \\
Protocols for huéspedes, and hospice philoxenia \\
As well as science, landscape, custom, way of life-- \\
In short, becoming those gold men of letters, who \\
To Andalusian soil gathered knowledge in their travels \\
Cross the cultures.

(Past-tense playing Perhacs, pleas to coffee date: \\
Five minutes can you spare me, girl; You'll get Eternity.)

Kiss me darling, as I fly. \\
From Death to Resurrection lie: \\
Ye, I had known the natural cycle \\
Sunlit seasons, springtime tidal. \\
Never, til now, in Catholic Europe \\
Did I know their rite \& symbol, \& \\
Swearing in a clearing, under God's first temple \\
That I'd bridge the basalt with the birdsong nimble \\
\qquad --\& other oaths, which do not scan-- \\
Of permanent poetics: what can last \& what is beautiful \\
And what is ever slipping lost, \\
Into unrecovered past.

For who else would report--it's not a matter of could--that chatty ``ciao'', informal, lost its whiff of offense, being constantly invoked by tourists til the mothertongue was chastened?

And who else would report that CaliValley apps were sync'ing up the world, teaching protocols and virtues; graphics, language, system?

--If there are no walls, there are no names-- \\
We're still hung up on Charles, contra native Paz, \\
Who saw in linèd borders only stoppèd separation: \\
Said, The mill? It squeeze juice from life; \\
He could see the grain collecting--All his
Cuartos, calles, ruas, rooms divided \\
Man from man, \& from himself, a violence \\
Mourning ``nuestra unidad''-—an unidad perdida.

O homogenocene! \\
Our Whitman's world, spanned \\
Except as farce at first \& second nightmare.

To navigate a gridded street, \\
And choose between two turns like Frosted Flakes. \\
Do streets constrain us, or enable passage? \\
One need only hack, like Carvajal, \\
Through undergrowth to know the difference. \\
And the merchants' code of choice? \\
Now an ethic of consent, argued by dissenting voice. \\

So all agreed-to's fine, \\
\qquad \& that which isn't, isn't. \\
How simple is what simple does, \\
Such beauty in its symmetry, \& \\
Power, then, is set aside; \\
Its problem now is prymary.

Wonder: Who has set the table? \\
When \& why assigned the labels?
