% This section is an introduction to, & description of,
% Barcelona: its architecture, flora, and anti-tourist sentiment.

% Unlike the Brazil sections, or even Vuelo, there is no real
% First person. The "foreigners kill yourself" graffiti
% Is tonally jarring; whether this is desirable or not is
% a separate question.

% ExSci status: None. Very little self; the poet-narrator
% has shrunk and is merely a set of eyes and ears.

``The straight line belongs to men; \\
The curved line, to God.'' \\
\hfill --Gaudi

--One American \\
--The Woman Who Loves Him, \\
--In a City That Despises them\footnote{W. Stillman.}

Not so romantic as ``Quiéreme Siempre''; \\
Still, the centre has its charms-- \\
Gulls in the Art Nouveau -opolis: \\
Temple of curves; \\
Porphyry hardrock.

Dawngress early to the hardbreakers-- \\
--La mar! La mére! \\
Past balcon undulation, \\
Meltwax colonnade, an irongrid \\
So intricate \& coiled.

Condensation's coral wake-- \\
Contrails cross behind the church \& \\
Catching pink dawn, catch on fire, light the \\
Spire while below the palmfronds cloister a capela; \\  
Servants of the Godly sing, cross \\
El Mercado Santa Catarina, \\
Built on catenated monastery, \\
Keeping former cloistered quadrille.

Old men carry fronds \\
I'm fond of them--I'd be the friend \\
Of any who might share their youth.

And in Gracia, wisteria are \\
All in bloom, as like as California. \\
Early still for diasporic magnols; \\
Just in time for citrus squeeze \& 
Concrete scratching: \\
``Foreigners, just kill yourselves.'' \\
In English, natch--``eunt domus.''\footnote{And go home they do--to the distress of the ministerium turismi.}
% Does the Eunt Domus bit still make sense, if the graffiti's gramatically correct? 
Sgraffiti on the walls at Vicens \\
Iron gate palmetto, where palmettos one day stood an \\
Ornament (``Que exotique!'') in gardens \\
Low an Arab smoking room, all \\
Built on boom years' short-lived edge, \\
A blight not yet arrived in Cataloñan vines: \\
The decade fore the border-cross \\
Before the phylloxera's frost.

% Abrupt ending