% After the sun sets on Sagrada,
% The narrator looks up at the moon, perhaps
% From some Spanish plaza, and contemplates
% Keats's negative capability and Prynne's poetry
% And wonders about a diffusion, rather than crystallization of form.

As Red Pine, staring out at sunset, summons Sixteen\-/Contemplationed Sutras, \\
So I think, in lunar gaze, of Prynne-- \\
His quiet night all bound in rising-falling; \\
Grasping, letting go; a fidgeting \& flowing.

``The continuing patience \\
dilating into forms so \\
much more than compact.'' \\

So much more than cómpact, \\
Whispers Aeryn Sun, \\
A memory (it brings me back)-- \\
I nearly had a self once. \\
Then I grew bored with brandings' borders, \\
Only saw their wild lack.

``The quiet
suggests that the act taken
extends so much further, there
is this insurgence of form:
we are more pliant than the mercantile notion 
of choice will determine.''

It was less like dying, and more like diffusion, \\
In the sense of freedom. Open spaces have their own virtue, which the densest-set artifacts\footnote{UV-measured silicone circuits.} of man do not approach.

For consent is not enough, if our identies are fashioned \\
For us. If they hold place in a system of social positions, \\
Which cannot be surrendered but, perhaps, transcended.

Is this, I thought, the incapacity of Keats? \\
A wide personal vacancy, allowing us to become \\
The extent of all the wishes now too far behind us, \\
A community of wish.

So now I'm learning: \\
Of fluorescence--versus incandescence \\
Lit up, glowing; take the picture \\
Fore the waves disperse, senescent. \\
So I'm draining cup \& doubting; \\
Judging each my muscle movements \\
As if they were aspirants \\
To founding some new life-long habit.

So I'm vowing: Never to be bound to any wheel \\
But what which keeps the grainheap growing.

\secdiv

Pah! It's but an hour later-- \\
Ere I have forgot it.