% The pilgrim visits the Sagrada, and finds the tourism empty, but also that a strong & strange magnetic power emanates from the cathedral.

% The below attaches to Barcelona section, on grapeblight.
Pale sapsucker. Yellow \\
Bellies, galling girdlers. \\
They used American immunology \\
In their hybrid grafts \\
So to save tradition.

This city of bas reliefs, \\
Mandalas in the cement suelo, \\
Lucid moments where you swear you see it all, \\
Then woozy slip below the waves of laggèd time.

At the main attraction, \\
No one looks at the main attraction. \\
Just collect pictures, vemödalen, to \\
Spare sight's labor, mem'ry's burden. \\

No one looks at the pictures later either--just shows them off to fam'ly, friends, and it makes you wonder what we're here for, on the planet I mean.

The stones not fully formed, the flowers \\
Still emerging from their undistinguished mass \\
A time of carving stones \\
And ``is'' a process of becoming.

And the pillars of the worldtemple \\
Are still held up by turtles; over portals, \\
Letters shaped from porticurling vine \\
Spelled OPUS, DEUS, 'pending from the side you saw it \\
And inside, wheat sprouts from the  \\
Baldachin of crucifixion, while around \\
An arbolith, and ceiling?  \\
Star\&sunseedvorticeseventhorizon \\
Irradiate \& rotate, powergenerate \& sucked \\
As lightcollapse to pinholed darkness.

Here is the transmission center. \\
Here is the whorlding vortex.

Stepping out as sky became a dusted spectrum, \\ 
Outside, cobweb catchfalls draped from \\
Still-in-progress towers, \\
Of the stony script-carved ledger.

