I wanted an accounting \\
Of how strong ships wreck \\
On subtlehidden stones. 

I wanted an accounting \\
Of how many great composers \\
Never found a venue, \\
Never found a patron, \\
Never found their players.

I was done with watercooler writing-- \\
Seedy news-- \\
The sidelines broadcast was OK, but \\
Shouldn't I be choosy with the games I chose to cover?

Anyway, \\
The best were all tacticians \\
Little soap, \& not a lot of sugar. \\
Surface near-implacable, \\
Uncrackable \& placid as the Catalan brûleé was eating in my decadence. 

Stephen said, Look, \\
If you're not always trying \& failing \\
To pay attention to near \\
Everything in life then \\
What are you doing?

Stephen said, \\
Too many big brave faces, \\
Scared of what might peek through pinhole \\
If they close their eyes.

And that the path was a mix of light and shadow, \\
And if that made the path a metaphor, fine.\footnote{T. Hoagland.}
And that Beeffalo, the abbey's dog, wrote poetry, in his rosemary bush, and rode a bike to town. \\
I'm getting a head of myself. Well then, I get ahead of myself.

The spirits argued with each other, \\
Shamed and cheered me from my shoulders; \\
Civic dust had set. \\
Me \& Newton \& conchas.

A sky full of ghosts-- \\
Light still traveled after the body was gone-- \\
Or at least the body's form-- \\
Since substance equaled pattern.\footnote{``The holiness of saints survives the body [such that] it is an effective power for healing and blessing even after death...'' (Deborah Kapchan, ``Henna and Tatoo,'' adapted.}

Was all this work not Christian, much like Bryan Johnson? \\
Sacrifice the now to chance forever on a dying sun?

A name in water never wrecks.