Tarragona--
Much like Barcelona, once
Bipolarized, to port \& fort, \\
To introspect \& interface-- \\
And a road to link them. \\
Like foce, gullet, gut; or like \\
A barbell, public-private, \\
First in steady stepping gress \\
To specialization.

This neverending ludos, \\
Self-distinction, seeking \\
Econicheconstruction \\
That guard a goal with equal spacing, \\
Field's zone o'coverage \\
Or like flower petals, radiant, \\
Do emanate from center \\
Seeking yet-uncaptured sun, while \\
Tethered in Augustan walls the \\
Poppy bloodred, rooted pared-- \\
Old stone \& young grass while \\
Mourning's ``Dove?'' coos in triple-time, \\
Oo-Oooooo-Oooo, \\
Playing hard to get, near cochineal, \\
Among the fruits of a colony feline.

Past Miocene limestone, bossaged ashlar rows and quoins, and azure waves, descendent by misrecognition, from the olden golden gules, we strolled; \\
She talked of liquifying, in the finance sense: \\
She talked of flowing fluids, freezing over; \\
Talked expansion and contraction. \\
I was always looking down, wary of dogshit, tired of looking down, and weary of dogshit. \\
Drank sangre to revitalize, in wooden chairs. \\
Everywhere the talk of stock all falling \\
Everywhere the morning doves in mourning \\
And no more children in the cafes or the flights.

\secdiv

I must've been sundrunk \& sleepdeprived, \\
To buy that goddamn hat. 

Soft light on creamstone, \\
Smell of oranges--cleaning fluid? \\
Gentle heel-tap on marble alley echo \\
Pinnate leaflets in a breezefall, carries,
Wheels onto sea which separates, as well connects. \\

I wanted an accounting \\
Of how strong ships wreck \\
On subtlehidden stones. 

I wanted an accounting \\
Of how many great composers \\
Never found the players to perform their music.

I was done with watercooler writing-- \\
Seedy news-- \\
The sidelines broadcast was OK, but \\
Shouldn't I be choosy with the games I chose to cover?

Anyway, \\
The best were all tacticians \\
No soap, \& not a lot of sugar. \\
Their surface as implacable, \\
Uncrackable \& placid as a crème brûleé.

He said, \\
Well yeah-- \\
And if you're not always trying \& failing \\
To pay attention to near \\
Everything in life then \\
What are you even doing?

He said, \\
Too many big brave faces, \\
Scared of what might peek through pinhole \\
If they close their eyes.

The spirits argued with each other, \\
Shamed and cheered me from my shoulders; \\
Civic dust had set. \\
Me, 'n Newton, 'n conchas \\
A sky full of ghosts, \\
Lights still traveling after the body was gone. \\
Or at least the body's form, \\
If substance equals pattern.